\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kashif Ali Khan} & Mobile: (91) 6306868361 \\
  \href{https://topmate.io/kashif_ali_khan}{topmate.io/kashif\_ali\_khan} & \href{mailto:kashifalikhan093@gmail.com}{Email: kashifalikhan093@gmail.com} \\
  \href{https://github.com/kashifalikhan36}{github.com/kashifalikhan36} & \href{https://www.linkedin.com/in/kashif-ali-khan}{LinkedIn: linkedin.com/in/kashif-ali-khan} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Experienced Software Developer skilled in AI integration, cloud technologies, and project leadership. Proven track record in designing high-efficiency AI solutions for industrial applications, guiding teams, and fostering cross-functional collaboration in technical and business strategy. Recognized for innovative projects and contributions to digital transformation.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Axis Institute of Technology and Management}{Uttar Pradesh, India}
      {B.Tech in Computer Science Engineering; GPA: 7.8}{2023 -- Present}
  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Best Mould Machine and Engineering Works}{Uttar Pradesh, India}
      {Support Engineer}{July 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered Generative AI Software}
          {Developed AI-powered software for streamlined 2D CAD model creation on CNC machines, utilizing Azure Virtual Machines and APIs, boosting production efficiency by 25\%.}
        \resumeItem{Created CAD Models}
          {Designed 100+ CAD models of shoe dye and related materials.}
      \resumeItemListEnd

    \resumeSubheading
      {Topmate Sessions}{Hybrid}
      {Technical Mentor and Interview Coach}{April 2021 -- May 2023}
      \resumeItemListStart
        \resumeItem{Facilitated Technical and Career Guidance}
          {Conducted 24+ sessions on interview preparation, technical skills development, and business strategy, contributing to enhanced job readiness and technical acumen among participants.}
      \resumeItemListEnd

    \resumeSubheading
      {Umeed – A Drop of Hope (NGO)}{Kanpur, India}
      {Marketing, HR, and Finance Intern}{January 2022 -- February 2022}
      \resumeItemListStart
        \resumeItem{Orchestrated Volunteer Recruitment and Fundraising}
          {Spearheaded recruitment drives and organized fundraising initiatives, achieving 100\% of targeted funding goals for community projects.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Blessi Voice Assistant}
      {Developed a voice-activated personal assistant using Azure Cognitive Services, supporting multiple languages. This innovation drove a 20\% increase in user engagement over six months by improving accessibility.}
    \resumeSubItem{SketchCad-AI for Industrial Design}
      {Engineered a scalable AI solution for automated 2D CAD model generation in industrial settings, leveraging Azure cloud infrastructure for high performance and scalability.}
    \resumeSubItem{Awaiki-AI Educational Transformation}
      {Constructed an app to convert YouTube lectures into eBooks and audiobooks, winning the Hack4Earth hackathon, promoting educational transformation with 500+ downloads achieved.}
    \resumeSubItem{GPT-Scrap Integration Tool}
      {Devised a bespoke scraping tool for seamless ChatGPT integration without requiring an API key, leading to a 25\% decrease in processing time and improved cross-device functionality.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages}{: Python, JavaScript, C, SQL, Java, C++} \\
     \textbf{Cloud and AI Technologies}{: Azure, FastAPI, AutoCAD, Git, TensorFlow, PyTorch} \\
     \textbf{Development Tools}{: Git, Visual Studio Code, Jupyter Notebook, Power BI} \\
     \textbf{Leadership and Project Management}{: Team Collaboration, Mentorship, Digital Transformation}
   }
 \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS------------
\section{Achievements}
 \resumeSubHeadingListStart
    \resumeItem{1st Place, HBTU Mini Hackathon (GDG Collaboration)}{Led team in project development, achieving first place.}
    \resumeItem{Honourable Mention, Hack4Earth Hackathon}{Recognized for innovative AI-driven educational solution.}
    \resumeItem{Certifications}{IS Audit and Controls - HKU; Programming for Everybody (Python) - University of Michigan.}
 \resumeSubHeadingListEnd

\end{document}
